---
title: "BacPoSSR Tutorial"
author: "Izumi Ando"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial_BacPoSSR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BacPoSSR)
```

## Introduction
loading package, viewing functions, calling help docs, listing datasets, calling rshiny

## Functionality
go through the functions using the sample dataset

### Step 0 : Load Data
### Step 1 : Multiple Component Analysis (MCA) on Unfiltered Dataset
### Step 2 : Filter Data
### Step 3 : MCA on Filtered Dataset

## Referencing this Package

Please use the following citation to reference this package.
<br>

- Ando, I. (2024) BacPoSSR: Filtering Tool to Reduce Population Structure Signal in Bacterial Genotype-Phenotype Analysis Data. Unpublished. https://github.com/izumiando/BacPoSSR

## References for the Development of this Package

- Chang W, Cheng J, Allaire J, Sievert C, Schloerke B, Xie Y, Allen J, McPherson J, Dipert A, Borges B (2024). _shiny: Web Application Framework for R_. R package version 1.9.1, <https://CRAN.R-project.org/package=shiny>.

- Karlsen, S. T., Rau, M. H., Sánchez, B. J., Jensen, K., & Zeidan, A. A. (2023). From genotype to phenotype: Computational approaches for inferring microbial traits relevant to the food industry. FEMS Microbiology Reviews, 47(4), fuad030. https://doi.org/10.1093/femsre/fuad030

- Lê S, Josse J, Husson F (2008). “FactoMineR: A Package for Multivariate Analysis.” Journal of Statistical Software, 25(1), 1–18. doi:10.18637/jss.v025.i01.

- Lees, J. A., Galardini, M., Bentley, S. D., Weiser, J. N., & Corander, J. (2018). pyseer: A comprehensive tool for microbial pangenome-wide association studies. Bioinformatics, 34(24), 4310–4312. https://doi.org/10.1093/bioinformatics/bty539

- Oksanen J, Simpson G, Blanchet F, Kindt R, Legendre P, Minchin P, O'Hara R, Solymos P, Stevens M, Szoecs E, Wagner H, Barbour M, Bedward M, Bolker B, Borcard D, Carvalho G, Chirico M, De Caceres M, Durand S, Evangelista H, FitzJohn R, Friendly M, Furneaux B, Hannigan G, Hill M, Lahti L, McGlinn D, Ouellette M, Ribeiro Cunha E, Smith T, Stier A, Ter Braak C, Weedon J (2024). _vegan: Community Ecology Package_. R package version 2.6-8, <https://CRAN.R-project.org/package=vegan>.

- R Core Team (2024). _R: A Language and Environment for Statistical Computing_. R Foundation for Statistical Computing, Vienna, Austria. <https://www.R-project.org/>.

- Sievert C, Cheng J, Aden-Buie G (2024). _bslib: Custom 'Bootstrap' 'Sass' Themes for 'shiny' and 'rmarkdown'_. R package version 0.8.0, <https://CRAN.R-project.org/package=bslib>.

- Wickham H (2016). ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York. ISBN 978-3-319-24277-4, https://ggplot2.tidyverse.org.


```{r}
sessionInfo()
```
